|

### 2020-02-29 paper/paper.Rmd
we're getting there!

title: |
    New and old ways to chase a rabbit:  
    Differential item functioning detection methods
subtitle: |
    Ben Stenhaug  
    Stanford University
abstract: |
  summarize propose extensions insist as dif as student property and on communicating uncertainty
  <!-- https://tinyurl.com/ybremelq -->
header-includes: 
- \usepackage{amsmath}
- \DeclareMathOperator*{\argmax}{arg\,max} # for gini coefficient

@@

```{r child = "paper_2_dif_methods.Rmd"}
```

>>>>

title: |
    New and old ways to chase a rabbit:  
    Differential item functioning detection methods
subtitle: |
    Ben Stenhaug  
    Stanford University
abstract: |
  summarize propose extensions insist as dif as student property and on communicating uncertainty
  <!-- https://tinyurl.com/ybremelq -->
header-includes: 
- \usepackage{amsmath}
- \DeclareMathOperator*{\argmax}{arg\,max} # for gini coefficient
- \DeclareMathOperator*{\argmin}{arg\,min} # for gini coefficient

@@

```{r child = "paper_2a_anchor_items.Rmd"}
```

## Anchor points

```{r child = "paper_2b_anchor_points.Rmd"}
```
